---
title: "plot var clim maps"
author: "Dana K Briscoe"
date: "`r Sys.Date()`"
output: html_document
params:
  source: 'glorys'
  # source: 'gcm'
  # var: 'thetao'
  var: 'so'
  depth: '_0m'
  scenario: 'ssp26'
  # scenario: 'ssp85'
  type: 'histclim'
  # stat: !r NULL
  stat: 'all_time_mean'
  location: 'full'
  pred_model: !r NULL
  # pred_model: 'growth_rate'
  # pred_model: 'CTX_rate'
  contour_labs: FALSE
  cbar_ticks_int: 2
  contours_major: TRUE
  contours_minor: FALSE
  cbar: TRUE
  include_title: TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load libraries ----
```{r}
## Load libraries ----
library(tidyverse)
library(raster)
library(purrr)
library(khroma)
library(RColorBrewer)
library(terra)
library(glue)
library(here)
```


## Source helper functions -----
```{r}

source(file.path(here() %>% dirname(), 'catalyst-bHABS','utils','catalyst_helper_functions.R')) # UPDATE ME!
source(here('utils','00_catalyst_helper_functions_MS.R'))
```

```{r}
## Source dynamically set param values based on var -----
source(here('utils', '00_params_rmd_plot_setup.R'))
```


## Set spp name -----
```{r}
params$spp <- 'G.polynesiensis'
```


## Load Clims List ----

```{r}

## Glorys var clim ----
clim_ras_histclim <- here('data', 'processed',
                      glue("glorys_all_time_mean_ras_full_1993-01-01_2024-12-31_{params$var}_0m.grd")) |> stack()

## GCM var clim
# update local param var for gcms
  if(params$var == 'thetao'){
    pvar = 'sst'
  } else if (params$var == 'so'){
    pvar = 'sss'
  }

## SSP 2.6 var clim ---
clim_ras_ssp26 <- here('data', 'processed',
                      glue("ssp26_{pvar}_ann_histclim_full_2070_2099_0m.grd")) |> stack()

## SSP 8.5 var clim ---
clim_ras_ssp85 <- here('data', 'processed',
                      glue("ssp85_{pvar}_ann_histclim_full_2070_2099_0m.grd")) |> stack()
```



### Downsample GLORYS to match GCMs?? -----
```{r}
### Spatially aggregate to match resolutions (1 x 1 degree gcm layer) ----
res <- res(clim_ras_ssp26)[1]
glorys_clim_resamp <- terra::resample(clim_ras_histclim, clim_ras_ssp26, method="bilinear")
```


## Get Diffs (Future - Current) ----
```{r}

# SSP 2.6 - Glorys ----
gg_clim_diff_ssp26_glorys <- clim_ras_ssp26 - glorys_clim_resamp

# SSP 8.5 - Glorys ----
gg_clim_diff_ssp85_glorys <- clim_ras_ssp85 - glorys_clim_resamp

```


## Get Diffs (Future 8.5 - Future 2.6) ----
```{r}
# SSP 8.5 - SSP 2.6 ----
gg_clim_diff_ssp85_ssp26 <- clim_ras_ssp85 - clim_ras_ssp26

```




### Set up plot params -----

#### Get world map ----
```{r}
# ## Set variables ----
mapdata <- ggplot2::map_data("world", wrap = c(-25, 335), ylim = c(-75, 75)) %>%
  filter(long >= 100 & long <= 210)

```

#### Set bbox -----
```{r}
bbox <- tibble(xmin = 120, xmax = 210, ymin = -60, ymax = 60, xstep = 10, ystep = -10)

```

#### Set color pals
```{r}
# color pal
smooth_rainbow <- khroma::colour("smooth rainbow")

cpal <- c(smooth_rainbow(length(seq(0, 0.25, length=100)), range = c(0, 0.9)), "#9e2a2b", "firebrick4")#, "#540b0e")
cpal <- rev(cpal)

# diff pal
div_pal <- rev(c(rev(brewer.pal(9, "YlOrRd")),"white", brewer.pal(9, "Blues")))
```


#### Set cbar legend title -----
```{r}
if(params$var == "thetao"){
  cbar_title = glue("SST\n({leg_units})\n")
} else if(params$var == "so"){
  cbar_title = glue("Salinity \n")
}
```


#### Local function to plot maps -----
```{r}

plot_clim_map <- function(ras, cbar_title = cbar_title){
  g <- plot_var(data= ras |> ras2pts(), 
              mapdata, bbox, cpal = rev(cpal), .legend = TRUE, .interp = TRUE)
  
  
   gg <- g + add_border() + resize_cbar(29) +
    # add_minor_contour_lines(df=ras |> ras2pts() |>
    #                           mutate(val = value, lon=x, lat=y),
    #                           contours = .contours_minor, linewidth = 0.5) +
    add_major_contour_lines(df=ras |> ras2pts() |>
                              mutate(val = value, lon=x, lat=y), 
                              contours = .contours_major, linewidth = 0.75) +
    add_basemap() 
  
  gg_formatted <- gg %>%
    addColorBar(., 
        c("white", rev(cpal[1:93])),
        limits=limits,   
        breaks=breaks,
        cbar_labels= breaks, #cbar_labels,
        
       plot_type = "continuous") +
      
    rename_legend(title = cbar_title)
  
  return(gg_formatted)
}
  
```




## Plot Clim Maps---
```{r}

.contours_major = contours_major

# glorys histclim - native res
gg_glorys_histclim_clim <- plot_clim_map(ras = clim_ras_histclim, #|> makePos(),
                                    cbar_title = cbar_title) 

gg_glorys_histclim_resamp_clim <- plot_clim_map(ras = glorys_clim_resamp, #|> makePos(),
                                    cbar_title = cbar_title) 

# gcm ssp2.6
gg_gcm_ssp26_clim <- plot_clim_map(ras = clim_ras_ssp26, #|> makePos(),   
                                    cbar_title = cbar_title)

# gcm ssp8.5
gg_gcm_ssp85_clim <- plot_clim_map(ras = clim_ras_ssp85, #|> makePos()
                                    cbar_title = cbar_title)

      
```


#### Local function to plot diff maps -----
```{r}

plot_clim_diff_map <- function(ras, cbar_title = cbar_title){

   g <-  plot_var(data=ras |> ras2pts(), mapdata, bbox, cpal = div_pal, .interp=TRUE, .legend = TRUE) 
   
   gg <- g + add_border() + resize_cbar(29) +
    #  
    # add_minor_contour_lines(df=diff_df |>
    #                           mutate(val = value, lon=x, lat=y),
    #                           contours = .contours_minor, linewidth = 0.5) +
    add_major_contour_lines(ras |> ras2pts() |>
                              mutate(val = value, lon=x, lat=y), 
                              contours = .contours_major, linewidth = 0.75) +
    add_basemap() 
  
    gg_formatted <- gg %>%
      addColorBar(., 
          div_pal[1:18],
          limits=limits,   
          breaks=breaks,
          cbar_labels=cbar_labels,
          
          plot_type = "continuous") +
      # labs(fill = ifelse(params$pred_model == 'growth_rate', 
      #                  'Difference in \nGrowth Rate \n(div/day)\n', 
      #                  'Difference in Total CTX \nProduction Rate \n(ng/ml/day)\n')) +    
    
      rename_legend(title = cbar_title)
    
  return(gg_formatted)
}
```


## Plot Clim Diff Maps---
### Set Diff Limits ----
```{r}

if(params$var == "thetao"){
  .contours_major <- seq(-6, 6, 1) 
  .contours_minor <- seq(-6, 6, 2)
  
  limits = c(-6,6)
  breaks = seq(-6,6,1) %>% round(., 2)
  cbar_labels = seq(-6,6,1)  %>% round(., 2)

} else if(params$var == 'so'){
  .contours_major <- seq(-2, 2, 1) 
  .contours_minor <- seq(-2, 2, 0.5)
  
  limits = c(-2,2)
  breaks = seq(-2,2,0.5) %>% round(., 2)
  cbar_labels = seq(-2,2,0.5)  %>% round(., 2)
}

```


```{r}


# SSP 2.6 - Glorys ----
gg_clim_diff_ssp26_glorys_clim <- plot_clim_diff_map(ras = gg_clim_diff_ssp26_glorys, 
                                    cbar_title = cbar_title) 

# SSP 8.5 - Glorys ----
gg_clim_diff_ssp85_glorys_clim <- plot_clim_diff_map(ras = gg_clim_diff_ssp85_glorys, #|> makePos(),   
                                    cbar_title = cbar_title)

# SSP 8.5 - SSP 2.6 ----
gg_clim_diff_ssp85_ssp26_clim  <- plot_clim_diff_map(ras = gg_clim_diff_ssp85_ssp26, #|> makePos()
                                    cbar_title = cbar_title)

```


### Save with Pos Preds ----
```{r}

gg_list <- list(gg_glorys_histclim_clim, 
                gg_glorys_histclim_resamp_clim, gg_gcm_ssp26_clim, gg_gcm_ssp85_clim,
                gg_clim_diff_ssp26_glorys_clim, gg_clim_diff_ssp85_glorys_clim, gg_clim_diff_ssp85_ssp26_clim
                )


names(gg_list) <- c(glue('clim_map_histclim_glorys_{params$var}_pos_vals'),
                    glue('clim_map_histclim_glorys_resamp_{params$var}_pos_vals'),
                    glue('clim_map_ssp26_{params$var}_pos_vals'),
                    glue('clim_map_ssp85_{params$var}_pos_vals'),
                    
                    glue('clim_map_diff_ssp26_glorys_{params$var}_pos_vals'),
                    glue('clim_map_diff_ssp85_glorys_{params$var}_pos_vals'),
                    glue('clim_map_diff_ssp85_ssp26_{params$var}_pos_vals')
                    
                    )


## Save pngs -----
gg_fnames <-  here('figs', glue('{names(gg_list)}.png')) |> as.list()

## save - this works (so does the above commented out option)
walk2(
  gg_fnames,
      gg_list,
  \(path, plot) ggsave(path, plot, width = 8)
)
  
```

## Crop Figs ----
### Sort Files in Chron Order
```{r}
# create movie
library(gtools)


# List plots files
flist <- list.files(here('figs'),pattern = "clim_map",full.names=T)
plot_files <- flist#[grepl(glue("_{env_info$eov}"), flist, fixed=TRUE)] 

plot_files_extent <- plot_files#[grepl(p_extent, plot_files, fixed=TRUE)] 

pfiles <- plot_files_extent[order(basename(plot_files_extent))]

pfiles <- gtools::mixedsort(pfiles)

```

# Crop PNG Frames
```{r }
# #intermediate step to crop PNG file and reduce negative space

## use crop image source function ------
source(here('utils','crop_image.R'))
crop_image(pfiles)

```



## Save RData ----
```{r}
## Save rdata ---- (for ms fig formatting)
save(
  gg_glorys_histclim_clim, 
  gg_glorys_histclim_resamp_clim, gg_gcm_ssp26_clim, gg_gcm_ssp85_clim,
  gg_clim_diff_ssp26_glorys_clim, gg_clim_diff_ssp85_glorys_clim, gg_clim_diff_ssp85_ssp26_clim,
  
  file = here('data', 'gg_data', glue('gg_clims_and_clim_diffs_{params$var}.rdata')))

```

