---
title: "Catalyst Format MS Figures"
author: "Dana K Briscoe"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
params:
  # location: 'nz'
  # location: 'japan'
  location: 'full'
  pred_model: 'growth_rate'
  # pred_model: 'CTX_rate'
  # out_dir_plots: '../figures/final_figs'
  contour_labs: TRUE
  fig_out_ext: '.png'
  # fig_out_ext: '.jpeg'
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    eval = TRUE,
    message = FALSE,
    warning = FALSE,
    dpi = 300,
    fig.align = "center",
    fig.height = 9
    )

# See Options: knitr::opts_chunk$get()
```

## Load libraries ----
```{r libraries, warning=FALSE,message=FALSE}
library(tidyverse)
library(raster)
library(ggplot2)
library(stringr)
library(khroma) # color pal
library(maps)
library(sf)
library(patchwork)

library(cowplot)

library(fontawesome)
# library(rsconnect)
library(rmarkdown)

library(patchwork)
```


## Source helper functions -----
```{r helper-funcs}
source(file.path(here() %>% dirname(), 'catalyst-bHABS','utils','catalyst_helper_functions.R')) # UPDATE ME!
source(here('utils','00_catalyst_helper_functions_MS.R'))
```


## Set spp name -----
```{r}
params$spp <- 'G.polynesiensis'
```



## Set bbox -----
```{r set-bbox}
# set bbox based on filename location
  if (params$location == "japan") {
    bbox <- tibble(xmin = 120, xmax = 160, ymin = 15, ymax = 60, xstep = 10, ystep = 10)
  } else if (params$location == "nz") {
    bbox <- tibble(xmin = 160, xmax = 210, ymin = -15, ymax = -60, xstep = 10, ystep = -10)
  } else if (params$location == 'full'){
    bbox <- tibble(xmin = 120, xmax = 210, ymin = -60, ymax = 60, xstep = 20, ystep = 20)#-10)
  }
```


## Load Files ----

```{r}
fpattern = c('gg_clims', params$pred_model)

flist = list.files(here('data', 'gg_data'), pattern = paste0(fpattern, collapse="|"), full.names = T) 

lapply(flist, load, environment())
```


<!-- ```{r} -->
<!-- horizontal_g_legend <- readRDS(file = str_c("../data/processed/pred_outputs/draft_pred_2070_2099_', params$pred_model", "_", params$pred_model, "_", params$location,"_legend_only.rds")) -->
<!-- ``` -->

## Define gg Funcs
```{r ggfuncs}
resize_cbar <- function(x){
    list(
        guides(fill = guide_colourbar(barheight =x, ticks = TRUE,
        frame.colour = "black", ticks.colour = "black"))
    )
}

add_border <- function(size=2){
  list(
      theme(panel.border = element_rect(colour = "black", fill=NA, size=size))
  )
}

format_subtitle <- function(size="14"){
  list(
    theme(plot.subtitle=element_text(size=size, hjust=0.5, face="bold", color="black"))
  )
}

format_plot_tag <- function(loc, size=5, color = "white", label = "A"){
  list(
        annotate("text", 
             x = 123.5,
             y = 57, 
             label = label, col = color, size = size)
  )
  
}

bold_all_text <- function(face="bold"){
  list(
    theme(text=element_text(size = 12, face=face))
  )
}  

```

```{r func-add-contour-labels}
add_contour_labels <- function(ras, .contours = .contours_major, 
                               nudge_x=0, nudge_y=0, line_col="snow"){
  addContours_major_nudge(x = ., 
                            contours = getContours(ras, levels = .contours), 
                            c_show = .contours, bbox = bbox, 
                            line_size = 1.0, label_size=4, nudge_x=+0, nudge_y=+0,
                            contour_color = "snow")
}

```


## Define Single-Display Func (1-Panel)
```{r func-display-single-fig}
display_single_fig <- function(pright){
  
    pright <- pright +  
      labs(caption = '', x = '') +
      scale_x_continuous(
        breaks = seq(bbox$xmin + 10, (bbox$xmax - 10), 
                     by = bbox$xstep),
        labels = function(x) ifelse(x < 180, paste0(x, "°E"), 
                             ifelse(x > 180, paste0("", abs(make180(x)), "°W"), 
                             ifelse(x == 180, paste0(x, "°"), x)))
      ) + 
      scale_y_continuous(
        breaks = seq(bbox$ymin, bbox$ymax, by = bbox$ystep),
        labels = function(x) paste0(ifelse(x < 0, paste0(abs(x), "°S"),
                                    ifelse(x > 0, paste0(x, "°N"), x)))
      ) +
      theme(plot.subtitle=element_text(size=8)) +
      theme(legend.position="none") +
      add_border() + format_subtitle() +

      bold_all_text()
    

    plot_row <- (pright) 
    
    ret_p <-
      plot_row +
        plot_annotation(
          title = '',
          caption = '',
          theme = theme(plot.caption = element_text(hjust=0),
                        text = element_text(size = 12, face="bold"))
          ) + 
        plot_layout(
          guides = 'collect') 
    
    return(ret_p)
}
```

## Define Multi-Display Func (2-Panel)
```{r func-display-multi-figs-2panel}
library(patchwork)

display_multi_figs_2panel <- function(pleft, pright){
  
  
    pleft <- pleft + 
      labs(caption = '', x = '') +
      scale_x_continuous(
        # breaks = seq(bbox$xmin + 10, (bbox$xmax - 10), 
        breaks = seq(bbox$xmin + 20, bbox$xmax, by = bbox$xstep),
        labels = function(x) ifelse(x < 180, paste0(x, "°E"), 
                             ifelse(x > 180, paste0("", abs(make180(x)), "°W"), 
                             ifelse(x == 180, paste0(x, "°"), x)))
      ) + 
      scale_y_continuous(
        breaks = seq(bbox$ymin, bbox$ymax, by = bbox$ystep),
        labels = function(x) paste0(ifelse(x < 0, paste0(abs(x), "°S"),
                                    ifelse(x > 0, paste0(x, "°N"), x)))
      ) +
      theme(plot.subtitle=element_text(size=8)) +
      theme(legend.position="none") +
      add_border() + format_subtitle() +
      format_plot_tag(label = "A") +
      bold_all_text()
    
    
    pright <- pright +  
      labs(caption = '', x = '') +
      theme(axis.text.y = element_blank(),
           axis.ticks.y = element_blank(),
           plot.margin = unit(c(0.02, 0.03, 0.02, 0.03), "null"),
           legend.title=element_text(size=10.5, face = "bold"),
           axis.title.y = element_blank()) +
      scale_x_continuous(
        # breaks = seq(bbox$xmin + 10, (bbox$xmax - 10), 
        breaks = seq(bbox$xmin + 20, bbox$xmax, by = bbox$xstep),
        labels = function(x) ifelse(x < 180, paste0(x, "°E"), 
                             ifelse(x > 180, paste0("", abs(make180(x)), "°W"), 
                             ifelse(x == 180, paste0(x, "°"), x)))
      ) + 
      # resize_cbar(18) +
      add_border() + format_subtitle() +
      format_plot_tag(label = "B") +
      bold_all_text()
    
    plot_row <- (pleft + pright) 
    
    ret_p <-
      plot_row +
        plot_annotation(
          title = '',
          caption = '',
          theme = theme(plot.caption = element_text(hjust=0),
                        legend.title = element_text(size = 12))
          ) + 
        plot_layout(
          guides = 'collect') 
    
    return(ret_p)
}

```

## Define Multi-Display Func (3-Panel)
```{r func-display-multi-figs-3panel}

display_multi_figs_3panel <- function(pleft, pcenter, pright){
  
  
    pleft <- pleft + 
      labs(caption = '', x = '') +
      scale_x_continuous(
        # breaks = seq(bbox$xmin + 10, (bbox$xmax - 10), 
        breaks = seq(bbox$xmin + 20, bbox$xmax, by = bbox$xstep),
        labels = function(x) ifelse(x < 180, paste0(x, "°E"), 
                             ifelse(x > 180, paste0("", abs(make180(x)), "°W"), 
                             ifelse(x == 180, paste0(x, "°"), x)))
      ) + 
      scale_y_continuous(
        breaks = seq(bbox$ymin, bbox$ymax, by = bbox$ystep),
        labels = function(x) paste0(ifelse(x < 0, paste0(abs(x), "°S"),
                                    ifelse(x > 0, paste0(x, "°N"), x)))
      ) +
      theme(plot.subtitle=element_text(size=8)) +
      theme(legend.position="none") +
      add_border() + format_subtitle() +
      format_plot_tag(label = "A") +
      bold_all_text()
    
    pcenter <- pcenter + 
      labs(caption = '') +
      scale_x_continuous(
        # breaks = seq(bbox$xmin + 10, (bbox$xmax - 10), 
        breaks = seq(bbox$xmin + 20, bbox$xmax, by = bbox$xstep),
        labels = function(x) ifelse(x < 180, paste0(x, "°E"), 
                             ifelse(x > 180, paste0("", abs(make180(x)), "°W"), 
                             ifelse(x == 180, paste0(x, "°"), x)))
      ) + 
      theme(legend.position="none",
           axis.text.y = element_blank(),
           axis.ticks.y = element_blank(),
           axis.title.y = element_blank()
           ) +
      add_border() + format_subtitle() + 
      format_plot_tag(label = "B") +
      bold_all_text()
    
    
    pright <- pright +  
      labs(caption = '', x = '') +
      theme(axis.text.y = element_blank(),
           axis.ticks.y = element_blank(),
           plot.margin = unit(c(0.02, 0.03, 0.02, 0.03), "null"),
           legend.title=element_text(size=10.5, face = "bold"),
           axis.title.y = element_blank()) +
      scale_x_continuous(
        # breaks = seq(bbox$xmin + 10, (bbox$xmax - 10), 
        breaks = seq(bbox$xmin + 20, bbox$xmax, by = bbox$xstep),
        labels = function(x) ifelse(x < 180, paste0(x, "°E"), 
                             ifelse(x > 180, paste0("", abs(make180(x)), "°W"), 
                             ifelse(x == 180, paste0(x, "°"), x)))
      ) + 
      # resize_cbar(18) +
      add_border() + format_subtitle() +
      format_plot_tag(label = "C") +
      bold_all_text()
    
    plot_row <- (pleft + pcenter + pright) 
    
    ret_p <-
      plot_row +
        plot_annotation(
          title = '',
          caption = '',
          theme = theme(plot.caption = element_text(hjust=0),
                        text = element_text(size = 12))
          ) + 
        plot_layout(
          guides = 'collect') 
    
    return(ret_p)
}

```




## Fig 1: Current Preds vs. SSP 2.6 vs SSP 8.5 - 3 Panel -----------------------------

#### Clims: Current - SSP 2.6 Preds & Current - SSP 8.5 Preds (2-Panel) -----

```{r}
p_thetao_glorys_ssp26_ssp85_3panel <- display_multi_figs_3panel(
    pleft = gg_list_thetao[['clim_map_histclim_glorys_resamp_thetao']], 
    pcenter = gg_list_thetao[['clim_map_ssp26_thetao']],
    pright = gg_list_thetao[['clim_map_ssp85_thetao']]
    ) 
                                   
p_thetao_glorys_ssp26_ssp85_3panel <- p_thetao_glorys_ssp26_ssp85_3panel + resize_cbar(23)

### Save plot ----
ggsave(filename = str_c('plot_thetao_glorys_ssp26_ssp85_3panel_', 
                        params$location, "_draft_ms_fig",
                        params$fig_out_ext), 
       plot = p_thetao_glorys_ssp26_ssp85_3panel, 
       # height=9,
       width=13, bg='white',
       path = here('figs'))
```


```{r}
p_so_glorys_ssp26_ssp85_3panel <- display_multi_figs_3panel(
    pleft = gg_list_so[['clim_map_histclim_glorys_resamp_so']], 
    pcenter = gg_list_so[['clim_map_ssp26_so']],
    pright = gg_list_so[['clim_map_ssp85_so']]
    ) 
                                   
p_so_glorys_ssp26_ssp85_3panel <- p_so_glorys_ssp26_ssp85_3panel + resize_cbar(23)

### Save plot ----
ggsave(filename = str_c('plot_so_glorys_ssp26_ssp85_3panel_', params$pred_model, "_", 
                        params$location, "_draft_ms_fig",
                        params$fig_out_ext), 
       plot = p_so_glorys_ssp26_ssp85_3panel, 
       # height=9,
       width=13, bg='white',
       path = here('figs'))
```



## Fig 2: Current Preds vs. SSP 2.6 vs SSP 8.5 - 3 Panel -----------------------------

### Current vs SSP 2.6 vs SSP 8.5 Preds (3-Panel) -----
```{r p_glorys_ssp26-3panel}
p_glorys_ssp26_ssp85_3panel <- display_multi_figs_3panel(
    pleft = gg_glorys_histclim_pred, 
    pcenter = gg_gcm_ssp26_pred,
    pright = gg_gcm_ssp85_pred
    ) 
                                   
if(params$pred_model=="growth_rate"){
  p_glorys_ssp26_ssp85_3panel <- p_glorys_ssp26_ssp85_3panel + resize_cbar(21.5)
} else if(params$pred_model=="CTX_rate"){
  p_glorys_ssp26_ssp85_3panel <- p_glorys_ssp26_ssp85_3panel + resize_cbar(21)
}

### Save plot ----
ggsave(filename = str_c('plot_glorys_ssp26_ssp85_3panel_', params$pred_model, "_", 
                        params$location, "_draft_ms_fig",
                        params$fig_out_ext), 
       plot = p_glorys_ssp26_ssp85_3panel, 
       # height=9,
       width=13, bg='white',
       path = here('figs'))
```


## Fig 3: Current Preds vs. SSP 2.6 vs SSP 8.5 - 2 Panel -----------------------------

#### Diff Preds: Current - SSP 2.6 Preds & Current - SSP 8.5 Preds (2-Panel) -----
```{r p_ssp26_ssp85_diff_btwn_ssp26_ssp85_3panel}

p_ssp26_ssp85_diff_btwn_glorys_2panel <- display_multi_figs_2panel(
    pleft = gg_diff_ssp26_glorys_pred, 
    pright = gg_diff_ssp85_glorys_pred
    )

if(params$pred_model=="growth_rate"){
  p_ssp26_ssp85_diff_btwn_glorys_2panel <- 
    p_ssp26_ssp85_diff_btwn_glorys_2panel + resize_cbar(25)
} else if(params$pred_model=="CTX_rate"){
  p_ssp26_ssp85_diff_btwn_glorys_2panel <- 
    p_ssp26_ssp85_diff_btwn_glorys_2panel + resize_cbar(25)
}

### Save plot ----
ggsave(filename = str_c('plot_ssp26_ssp85_diff_btwn_glorys_2panel_', ... = 
                        params$pred_model, "_", 
                        params$location, "_draft_ms_fig",
                        params$fig_out_ext), 
       plot = p_ssp26_ssp85_diff_btwn_glorys_2panel, 
       # height=9,
       width=13, bg='white',
       path = here('figs'))
```


## Crop Figs ----
### Sort Files in Chron Order
```{r}
# create movie
library(gtools)


# List plots files
flist <- list.files(here('figs'),pattern = "plot_",full.names=T)
plot_files <- flist#[grepl(glue("_{env_info$eov}"), flist, fixed=TRUE)] 

plot_files_extent <- plot_files#[grepl(p_extent, plot_files, fixed=TRUE)] 

pfiles <- plot_files_extent[order(basename(plot_files_extent))]

pfiles <- gtools::mixedsort(pfiles)

```

# Crop PNG Frames
```{r }
# #intermediate step to crop PNG file and reduce negative space

## use crop image source function ------
source(here('utils','crop_image.R'))
crop_image(pfiles)

```
